On g~0~

### 2017-03-14 manuscript.Rmd
figures tidies; some new references; gmin analysis kerstiens etc
added simulate figure with and without g0

@barnard2013 makes the same assumption

@@

@@

@@

>>>>

@barnard2013 makes the same assumption, without any discussion of the possibility that daytime g0 might be different from nighttime conductance

@@

[@medlyn_reconciling_2011] does not develop theory for g0, instead adds it as a minimum conductancce because that's how it is!

When fitting a Ball-Berry type model, negative values are quite common. A typical approach is to avoid this by setting some value based on guesswork [e.g. @leuning_modelling_1990], which we assume is quite common when inspecting the many rounded values in the review by

The first Ball-Berry model did not have a g0

@@

[@leuning_critical-appraisal_1995]

@@

@rescodedios2016 early night gs much (much) lower than pre-dawn gs, in E. camaldulensis
@rescodedios2013 nighttime fluctuation gs independent of environment
